\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

\namesection{Ryan}{Tse}{8505 Wilkesboro Lane, Rockville MD, 20854 \\
\href{mailto:rytse@umd.edu}{rytse@umd.edu} | (240) 643-0657 | \href{https://rytse.github.io}{rytse.github.io}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

\section{Education} 

\vspace{0.125cm}

\sectionsep
\subsection{University of Maryland}
\descript{Freshman Electrical Engineering Major}
\location{2019-Present | College Park, MD}

\vspace{0.375cm}
\begin{tightemize}
    \item Partial Differential Equations
\end{tightemize}
\vspace{0.125cm}

\sectionsep
\subsection{Montgomery Blair \\ High School}
\descript{STEM Magnet Student}
\location{2015-2019 | Silver Spring, MD}

\vspace{0.125cm}
\begin{tightemize}
    \item Intro to Complex Analysis
    \item Multivariable Calculus
    \item Differential Equations
    \item Linear Algebra
    \item Mathematical Physics
    \item Intro to Quantum Physics
    \item Analysis of Algorithms
    \item Intro to Computational Methods
    %Intro to Organic Chemistry \\
\end{tightemize}
\vspace{0.125cm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\sectionsep
\section{Skills}

\vspace{0.125cm}

\subsection{Experienced}
Python \textbullet{} C \textbullet{} Java \textbullet{} Git \textbullet{} Linux \\
GNURadio \textbullet{} Autodesk Inventor \\
\sectionsep

\subsection{Familiar}
C++ \textbullet{} Matlab \textbullet{} R \textbullet{} Tensorflow \textbullet{} Keras \\
OpenAI Gym \textbullet{} OpenCV \textbullet{} \LaTeX
\sectionsep

\subsection{Novice}
Slurm \textbullet{} ROS \textbullet{} JavaScript \textbullet{} Groovy \\
AWS \textbullet{} GCP \textbullet{} AutoCAD
\sectionsep

\sectionsep
\section{Leadership}

\vspace{0.125cm}

\textit{blair3sat} President

\indent - 19 person, 4 subteam group

\vspace{0.125cm}

\textit{blair3sat} RF Instrument Lead

\indent - 4 person subteam

\vspace{0.125cm}

\textit{FRC Team 449} Software and Controls Subteam Lead

\indent - 5 person subteam

\vspace{0.125cm}

\textit{Troop 1449} Senior Patrol Leader

\indent - 35 person, 4 patrol troop

\sectionsep
\section{Links} 

\vspace{0.125cm}

GitHub:// \href{https://github.com/rytse}{\bf github.com/rytse} \\
LinkedIn://  \href{https://www.linkedin.com/in/rytse0}{\bf linkedin.com/in/rytse0} \\
Devpost:// \href{https://devpost.com/rytse}{\bf devpost.com/rytse} \\
% Twitter://  \href{https://twitter.com/rytse_}{\bf @debarghya\_das} \\

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

\section{Personal Summary}

\textit{Freshman electrical engineering major at the University of Maryland. Founder and former president and RF instrument engineer of an innovative high school CubeSat team. Currently pursuing advanced undergraduate research opportunities in the fields of digital signal processing, control, and machine learning. Eagle Scout for life.}

\sectionsep
\section{Work Experience}

\vspace{0.125cm}

\runsubsection{\href{https://www.i-a-i.com/}}{Intelligent Automation Incorporated} \\
% \descript{Naval Research Laboratory Summer Intern }
\location{Summer 2019 | Sensors, Signals and Systems Division | Intern}
Assisted in the hardware implementation of a bursty space-time continuous phase modulation receiver by analyzing quantization error. Assisted in developing indoor positioning system technology by modifying tracking filters to include IMU data.
\sectionsep

\runsubsection{\href{https://www.nrl.navy.mil/sed/branches/8240}{Naval Center for Space Technology}} \\
% \descript{Naval Research Laboratory Summer Intern }
\location{Summer 2018 | Naval Research Laboratory | Intern}
Developed an efficient bursty satellite ranging protocol in GNURadio. Applied control loops to correct for channel impairments and implemented packet protocols.
\sectionsep

\runsubsection{\href{https://www.nrl.navy.mil/lasr/content/mobile-autonomous-navy-teams-information-surveillance-and-search}{Laboratory for Autonomous Systems Research}} \\
\location{Summer 2017 | Naval Research Laboratory | Intern}
Researched deep learning-based approaches to vehicle trilateration, working with regression models and reinforcement learning agents. Author of Publication \cite{lps}.

\sectionsep

\section{Extracurriculars}

\vspace{0.125cm}

\runsubsection{\href{https://www.blair3sat.com/}{blair3sat}} \\
\location{2017 – Present | President, Founder, and RF Payload Engineer}
Developing a CubeSat to measure 3D ionospheric charge density profiles by receiving ground-based ionospheric sounders from space. Performing DSP for the instrument and leading the team in spacecraft engineering and fund seeking in an executive capacity. Secured \$6,000 of funding and two corporate partnerships in 6 months. Author of Publication [2].
\sectionsep

% \runsubsection{MBHS ~Systems} \\
% \location{2017 – Present | Student Researcher}
% Developing a reinforcement learning agent to solve incompressible flows more quickly by running RANS, LES, and DNS on a partitioning of the simulation domain.
% \sectionsep

\runsubsection{\href{https://robot.mbhs.edu/}{FIRST ~Robotics~ Challenge}} \\
\location{2015 - 2017 | FRC Team 449 | Software and Controls Lead}
Developed drivetrain control and automation software, lead the 2017 software team.
\sectionsep

\vspace{-0.35cm}

\runsubsection{\href{https://rockville1449.mytroop.us/}{Scouting}} \\
\location{2012 - 2018 | Boy Scout Troop 1449}
Eagle Scout, served as Senior Patrol Leader, Troop Quartermaster, and Patrol Leader.
\sectionsep

\section{Competitions} 
\vspace{0.25cm}
\begin{tightemize}
    \item \href{https://bit.camp/}{Bitcamp} 2019, built \href{https://devpost.com/software/owsf}{\textit{Open Weapon Site Finder}}, won \textit{Best Digital Forensics Hack}, runner up for \textit{Best Machine Learning Hack}
    \item Kaggle's \href{https://www.kaggle.com/c/mens-machine-learning-competition-2019/leaderboard}{Google Cloud \& NCAA 2019 ML Competition, placed 37th out of 866}
    % \item MathWorks Math Modeling Challenge 2019 Second Round Contender
\end{tightemize}
\sectionsep

\section{Publications}
\vspace{0.75cm}

\begin{thebibliography}{2}
\bibitem{lps} 
D. Lofaro, C. Taylor, R. Tse, and D. Sofge, “Wearable Interactive Display for the Local Positioning System (LPS),” In 19th ACM International Conference on Multimodal Interaction (ICMI 2017) Demonstration Session, ACM, 2017.

\bibitem{sirvlas}
R. Tse, L. Cui, P. Kim, S. Swain, B. Cohen, and G. Das. “Space-based Ionosonde Receiver and Visible Limb-viewing Airglow Sensor (SIRVLAS): A CubeSat Instrument Suite for Enhanced Ionospheric Charge Density Measurements,” Proceedings of the AIAA/USU Conference on Small Satellites, SSC19-WP2-14.
 
\end{thebibliography}

\end{minipage} 
\end{document}%  \documentclass[]{article}
